% LaTeX file for resume 
% This file uses the resume document class (res.cls)

\documentclass{res} 
%\usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
%\usepackage{newcent}   % uses new century schoolbook postscript font 
\setlength{\textheight}{9.5in} % increase text height to fit on 1-page 

\begin{document} 

\name{Lucas Langer\\[12pt]}     % the \\[12pt] adds a blank
				        % line after name      

\address{\bf  CONTACT
\\66 Wolseley Ave North, Montreal, QC, H4X1V7 \\Email: lucas.langer@mail.mcgill.ca
\\Cell: 1-438-491-7656}

\address{\bf LINKS 
\\  Github: lucaslanger}
                                  
\begin{resume}          
 
\section{EDUCATION}          
    McGill University, Montreal, QC  \\        
    Bachelor of Science, September 2014 - July 2017 (Expected)   \\       
    Mathematics and Computer Science
    CGPA. \textbf{3.97/4.0}          

 
\section{EXPERIENCE}
   \vspace{-0.1in}	
   \begin{tabbing}
   \hspace{2.3in}\= \hspace{2.6in}\= \kill % set up two tab positions
    {\bf Software Engineering Intern} \> Twitter \> {\bf Upcoming} January-April 2017\\
                          \> San Francisco, CA
   \end{tabbing}\vspace{-20pt}
    I will be interning with the Core System Libraries Team. They develop the back-end infrastructure for Twitter including Finagle, Util, Twitter Server, and Scrooge.
   
   \begin{tabbing}
   \hspace{2.3in}\= \hspace{2.6in}\= \kill % set up two tab positions
    {\bf Machine Learning Researcher} \> McGill RL Lab    \> May-September 2015\\
                             \> Montreal, QC
   \end{tabbing}\vspace{-20pt}      % suppress blank line after tabbing
    Designed, implemented, and tested a novel spectral learning algorithm for making predictions in partially observable environments. Applications include robotics, medical time-series, natural language processing, and more. 
    
   \begin{tabbing}
   \hspace{2.3in}\= \hspace{2.6in}\= \kill % set up two tab positions
    {\bf Volunteer Camp Counsellor} \> McGill Computer Science Camp \> July 2014\\
                          \>Montreal, QC
   \end{tabbing}\vspace{-20pt}
    Gave programming tutorials to graduating high school students. Helped design and organize robotics competitions (sumo-wrestling, maze navigation). 

\section{PUBLICATIONS}
	Lucas Langer, Borja Balle, and Doina Precup. "Multi-Step Predictive State Representations". Time Series Workshop, Neural Information Processing Systems (NIPS), December 11 2015 {\bf (Accepted)} 

\section{COMPUTER SKILLS}          
	Primary: Java, Python  \\
	Secondary: OCaml, C \\
	Web: HTML, CSS, Bootstrap \\
	Other: Bash, SQL, LaTeX        
 
\section{HONOURS AND AWARDS}          
    NSERC Research Award: \$5625   \\      
    Dean's Honour List: Top 10\%       
 
\section{EXTRACURRICULAR ACTIVITIES}
	Investment Committee, Stock Analyst Program  \\ 
	McGill Undergraduate Research Conference \\
	McHacks (flight simulator), CodeJam (recognizing faces)\\   
    Computer Taskforce Volunteer
    
\section{LANGUAGES}
	English: fluent  \\
	French: limited working proficiency \\
	German: limited proficiency

\end{resume}
\end{document}